Pillar 2 - Topic Modeling

### 2019-05-03 Pillar 2 - Topic Modeling.Rmd
clean Pillar 2

empty_titles <- course_titles %>% filter(`Course Title` == "")
```
####Uniform titles
We do not have the course codes for all courses, in that case we use the course titles as identifiers, for more pleasant display to the user, we will make course labels uniform, for unknown codes we give the label "unknown" and attatch the title as title. 
```{r attatch titles}
uniform_course_labels <- course_titles %>% mutate(`c_title`= case_when(is.na(`Course Title`) ~ `Course ID`,
                                              T ~ `Course Title`),
                         `Course ID` = case_when(str_length(`Course ID`) == 7 ~ `Course ID`,
                                                 T ~ "unknown"),
                         `Course Title` = c_title
                         ) %>% select(-c_title)
```
###Functions for internal faceting
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

@@

##Plots - Model Evaluation CHANGE TO CONFERENCE CODE
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin, data = tb_topic_model){

@@

##Best model
We extract the best model and use it to innitialise the the second run of LDA algorithm with more burns and iterations
```{r best model, eval = T}
catalogues_tm <- tb_topic_model %>% filter()
catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]

best_lda <- LDA(x = catalogue_dtm, 
                model = catalogue_lda, 
                control =  list(
                  nstart = 50,
                  seed   = 1 : 50, #must have length nstart
                  best   = TRUE,
                  burnin = 100,
                  iter   = 10000,
                  thin   = 2000) 
                )

save(best_lda, file = "./Output/catalogues_best_model.RDATA") 
```
##Best model pass to app
```{r}
load("./Output/catalogues_tmp_topic_model_tibble.RDATA")
load("./Output/catalogues_best_model.RDATA")

best_model <- tibble( 
  n_topic = 65
  ) %>%

  mutate(Origin     = "catalogues",
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

         #Fit Model
         Model  = list(best_lda),

@@

#App
For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words}
clean_kw <- function(kw_list){

@@

```
On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
```{r crop and clean TM for App}
app_topic_model <- test_topic_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
  mutate(kw = map(kw, .f = clean_kw))
```

##Convenience Vectors
For the app we also need to have a list of all courses and an example of a prospective semester
```{r for convenience}
# set seed
set.seed(1)

@@

```{r adding convenience vectors}
app_topic_model <- app_topic_model %>%
  mutate(`All Courses`     = course_all,
         `Sample semester` = course_following_semester)

#rm(course_all, course_following_semester)
```
## Saving files for APP
```{r app files}
# save(app_topic_model, file = "App/Recommender System/data_topic_models.RDATA")
```
# Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

  data.frame(d_beta) %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

} #repetition??? of inspect topics?

prepare_data_LDA_gamma <- function(d_gamma, level = Course){

  data_gamma <- data.frame(d_gamma) %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)

  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = `Course ID`)

  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                       filter(!is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)

  data_gamma <- data_gamma %>%
    group_by(facet, topic) %>%
      summarise(gamma = sum(gamma)) %>%
    filter(gamma > 0.05) %>%
    ungroup %>%
    arrange(facet, desc(gamma))

  return(data_gamma)

# Bet Distribution
test <- list()

a <-  names(distribution)[1]
test[[a]] <- lapply(distribution[[a]],
                      prepare_data_LDA_beta)

# Gamma Distribution
b <- names(distribution)[2]
test[[b]] <- lapply(distribution[[b]],
                    prepare_data_LDA_gamma)

test <- test_topic_model %>%
  mutate(preparedBeta = pmap(list(Beta), .f = prepare_data_LDA_beta),
         preparededGamma = pmap(list(Gamma), .f = prepare_data_LDA_gamma)
         )
test[["preparedBeta"]]
rm(a,b #,test
   )
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
  ggplot(aes(x = reorder_within(term,
                                by = beta,
                                within = topic),
             y = beta,
             fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, scales = "free") +
    scale_x_reordered() +
    labs(x = "Terms", y = "Beta", title = "Main Terms of each Topic") +
    coord_flip() +
    theme_light() +
    theme(plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "beta.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

visualize_LDA_gamma1 <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
    ggplot(aes(reorder_within(facet, 
                              by = gamma, 
                              within = topic), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma1.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

visualize_LDA_gamma2 <- function(data_prepared, id_plot = "test"){

  data_prepared %>%
    ggplot(aes(reorder_within(topic, 
                              by = gamma,
                              within = facet), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ facet, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
  #  labs(x = "Topics", y = "Gamma", title = "Main Topics of each Courses/Cluster") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

  ggsave(paste(id_plot, "gamma2.jpeg"),
         width = 16, height = 10, path = "Plots/Topic Model")

```{r LDA visualize all distrib, eval = F}
visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){

  # Beta distribution
  data %>% 
    prepare_data_LDA_beta %>%
    visualize_LDA_beta(id_plot = id_plot)

  # Gamma 1 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma1(id_plot = id_plot)

  # Gamma 2 distribution
  data %>% 
    prepare_data_LDA_gamma(level = !!ensym(level)) %>%
    visualize_LDA_gamma2(id_plot = id_plot)

```{r LDA visualize all level, eval = F}
visualize_LDA_all_level <- function(data, id_plot = "test"){

  data %>% 
    visualize_LDA_all_distrib(level = Course,
                              id_plot = paste(id_plot, "_course"))

  data %>% 
    visualize_LDA_all_distrib(level = Cluster,
                              id_plot = paste(id_plot, "_cluster"))

  data %>% 
    visualize_LDA_all_distrib(level = Concentration,
                              id_plot = paste(id_plot, "_concentration"))

### Plots
```{r LDA plot, cache = TRUE, eval = F}
load("LDA.RDATA")

LDA_description_5 %>% visualize_LDA_all_level(id_plot = "description_k5")

LDA_overview_5 %>% visualize_LDA_all_level(id_plot = "overview_k5")

LDA_manual_5 %>% visualize_LDA_all_level(id_plot = "manual_k5")
```

```{r label, eval = FALSE, eval = F}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))

  count(term, topic) %>%
  arrange(desc(n)) %>%

  filter(beta > 1e-3) %>%
  group_by(term) %>%
    mutate(n_topic = n(),
           beta = beta / n_topic) %>%
  group_by(topic) %>%
    top_n(10, beta)

  count(topic, term, wt = beta) %>%
  (term = term, document = topic, n = n) %>%
  group_by(topic) %>%
  top_n(10, tf_idf)

  group_by(term) %>%
  summarise(beta = sum(beta)) %>%
  arrange(desc(beta))

labels <- list(
  description_10 = "X"
)
```

```{r label bis, eval = FALSE}
visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
                              "Sociology", "Law", "Research", "International Politics",
                              "Philosophy", "Humanities"))

visualize_LDA(LDA_cluster_17, id_plot = "Cluster, k = 17 with labelled topics", facet = T,
              topic_names = c("Science/Knowledge", "Psycho", "Biology", "Chemistry", "Culture",
                              "Conflict", "Research", "Foreign Policy", "Arts", "Literature",
                              "Communication Skills", "Law", "Humanities", "Computer", "Economics", 
                              "Math", "Management and ?"))
visualize_LDA(LDA_cluster_25, id_plot = "Cluster, k = 25 with labelled topics", facet = T,
              topic_names = c(
                "Information", "Psycho", "Bio", "Chem", "Sociology",
                "History", "skills", "Europe", "Philosophy", "IR",
                "Conference", "Law", "Media", "Philosophy", "Economics",
                "Math", "Management and Literature", "Entrepreneurship", "Conflict", "Research",
                "Arts", "Computer Science", "Policy?", "Physiology", "Qual. Res."))
```

>>>>

empty_titles <- course_titles %>% filter(`Course Title` == "")
```
####Uniform course labels
We do not have the course codes for all courses, in that case we use the course titles as identifiers, for more pleasant display to the user, we will make course labels uniform, for unknown codes we give the label "unknown" and attatch the title as title. 
```{r attatch titles}
uniform_course_labels <- course_titles %>% mutate(`c_title`= case_when(is.na(`Course Title`) ~ `Course ID`,
                                              T ~ `Course Title`),
                         `Course ID` = case_when(str_length(`Course ID`) == 7 ~ `Course ID`,
                                                 T ~ "unknown"),
                         `Course Title` = c_title
                         ) %>% select(-c_title)
```
###Functions for internal faceting
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

@@

##Model Evaluation CHANGE TO CONFERENCE CODE
###Plots
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin, data = tb_topic_model){

@@

###Value
```{r best number of topics extraction}
n_topics_best_manuals    <- manuals_topic_model    %>% top_n(1, LogLikelihood) %>% pull(n_topic)
n_topics_best_catalogues <- catalogues_topic_model %>% top_n(1, LogLikelihood) %>% pull(n_topic)
```

##Best model
We extract the best model and use it to innitialise the the second run of LDA algorithm with more burns and iterations
###catalogues best model
```{r best catalogues tm, eval = T}
catalogues_tm <- tb_topic_model %>% filter(Origin == "catalogues")

catalogue_dtm <- catalogues_tm$DTM[[1]]

catalogue_lda <- catalogues_tm %>% filter(n_topic == n_topics_best_catalogues) %>% pull(Model) %>%.[[1]]

#Train best model 
catalogues_best_lda <- LDA(x = catalogue_dtm, 
                model = catalogue_lda, 
                control =  list(
                  nstart = 50,
                  seed   = 1 : 50, #must have length nstart
                  best   = TRUE,
                  burnin = 100,
                  iter   = 10000,
                  thin   = 2000) 
                )

save(catalogues_best_lda, file = "./Output/catalogues_best_model.RDATA") 
```
###manuals best model
NOTE: BEST MANUALS NUMBER OF TOPICS TO BE DETERMINED 
```{r best manuals tp, eval = F}
manuals_tm    <- tb_topic_model %>% filter(Origin == "manuals")

manual_dtm <- manuals_tm$DTM[[1]]

manual_lda <- manuals_tm %>% filter(n_topic == n_topics_best_manuals) %>% pull(Model) %>%.[[1]]

#Train best model
manuals_best_lda <- LDA(x = manual_dtm, 
                model = manual_lda, 
                control =  list(
                  nstart = 50,
                  seed   = 1 : 50, #must have length nstart
                  best   = TRUE,
                  burnin = 100,
                  iter   = 10000,
                  thin   = 2000) 
                )

save(manuals_best_lda, file = "./Output/manuals_best_model.RDATA") 
```

##Best model pass to app
```{r load best models, eval = F}
load("./Output/full_topic_model_tibble.RDATA") #contains both manuals and catalogues

#Alternatively:
#load("./Output/catalogues_topic_model_tibble.RDATA")

#Best models:
load("./Output/catalogues_best_model.RDATA")
load("./Output/manuals_best_model.RDATA")
```

```{r best models clean for app, eval = TRUE}
#helper function
get_best_lda <- function(Origin){
  if(Origin == "catalogues"){

    return (catalogues_best_lda[[1]])

  } else if(Origin == "manuals"){

      return(manuals_best_lda[[1]])
    }
}

best_model <- tibble( 
  n_topic = c(n_best_catalogues, n_best_manuals)
  ) %>%

  mutate(Origin     = c("catalogues", "manuals"),
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

         #Fit Model
         Model  = pmap(.l = list(Origin), .f = get_best_lda),

@@

###Save best model
```{r save best model, eval = TRUE}
save(best_model, file = "./Output/best_model.RDATA")
```

#App
For our recommender system, we pass the distributions, number of topics, origin, and key words to the app.
##Distributions and Key words
The function `clean_kw` removes stopwords from our key words.
```{r function clean key words, eval = TRUE}
clean_kw <- function(kw_list){

@@

```
On our `topic_model` tibble we filter only information relevant for the app, and apply `clean_kw` on our `kw` column
```{r crop and clean TM for App, eval = TRUE }
app_topic_model <- best_model %>% select(`Topic ID`, n_topic, Origin, Gamma, Beta, kw) %>%
  mutate(kw = map(kw, .f = clean_kw))
```

##Convenience Vectors
For the app we also need to have a list of all courses and an example of a prospective semester
```{r for convenience, eval = TRUE}
# set seed
set.seed(1)

@@

```{r adding convenience vectors, eval = TRUE}
app_model <- app_topic_model %>%
  mutate(`All Courses`     = list(course_all),
         `Sample semester` = list(course_following_semester),
         `Course Titles`   = list(course_titles) )

#rm(course_all, course_following_semester)
```
## Saving files for APP
```{r app files, eval = TRUE}
save(app_model, file = "App/Recommender System/app_model.RDATA")
save(app_model, file = "./Output/app_model.RDATA")
```
